Scalar on Function Regression \\ with Applications to Near-Infrared Spectography

### 2022-01-14 Presentation/slides.tex
Added links to slides

% Theme choice:
\usetheme{Berlin}
\usecolortheme{seahorse}

@@

	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}
		A random function $X(\omega)$ can be expressed in terms of its mean function and its Eigenfunctions:
		$$X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)$$

@@

		This is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of $X(\omega)$ and the Eigenfunctions can serve as a basis.
	\end{frame}

@@

	\begin{frame}{Functional Principal Component Analysis}

@@

@@

	\begin{frame}{Spectral Representation of Random Vectors}
		Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.

@@

		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[\xi_i(\omega)] = 0$
				\item $Var(\xi_i(\omega)) = \lambda_i$
				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
	\end{frame}

	\begin{frame}{Principal Component Analysis}
		A related concept is \textbf{Principal Component Analysis} (PCA).
		\vspace{0.2cm}

@@

		Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[Z_i(\omega)] = 0$
				\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
				\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
	\end{frame}

\end{document}

>>>>

% Theme choice:
\usetheme{Dresden}
\usecolortheme{whale}

@@

	\begin{frame}{Karhunen-Lo\'{e}ve Expansion}\label{KLE}
		A random function $X(\omega)$ can be expressed in terms of its mean function and its Eigenfunctions:
		$$X(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)$$

@@

		This is called the \textbf{Karhunen-Lo\'{e}ve Expansion} of $X(\omega)$ and the Eigenfunctions can serve as a basis. \\

		\hyperlink{spectral}{\beamergotobutton{Spectral Representation of Random Vectors}}
	\end{frame}

@@

	\begin{frame}{Functional Principal Component Analysis}\label{FPCA}

@@

		\hyperlink{PCA}{\beamergotobutton{PCA for Random Vectors}}
	\end{frame}

@@

	\begin{frame}{Spectral Representation of Random Vectors}\label{spectral}
		Let $X(\omega)$ be a random vector realizing in $\mathbb{R}^p$.

@@

		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[\xi_i(\omega)] = 0$
				\item $Var(\xi_i(\omega)) = \lambda_i$
				\item $Cov(\xi_i(\omega), \xi_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}

		\hyperlink{KLE}{\beamergotobutton{Karhunen-Lo\'{e}ve Expansion}}
	\end{frame}

	\begin{frame}{Principal Component Analysis}\label{PCA}
		A related concept is \textbf{Principal Component Analysis} (PCA).
		\vspace{0.2cm}

@@

		Then $Z_i(\omega) = \hat{\gamma}_i' X(\omega)$ is called the i'th principal component and
		\begin{multicols}{2}
			\begin{enumerate}
				\item $\mathbb{E}[Z_i(\omega)] = 0$
				\item $Var(Z_i(\omega)) = \hat{\lambda}_i$
				\item $Cov(Z_i(\omega), Z_j(\omega)) = 0$ for $i \neq j$
			\end{enumerate}
		\end{multicols}
		\hyperlink{FPCA}{\beamergotobutton{Functional Principal Component Analysis}}
	\end{frame}
\end{document}
